%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.7.2, 28 August 2024) written by LianTze Lim (liantze@gmail.com). Compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[9pt,a4paper,ragged2e,withhyper]{altacv} %ragged2e
%% AltaCV uses the fontawesome5 and simpleicons packages.
%% See http://texdoc.net/pkg/fontawesome5 and http://texdoc.net/pkg/simpleicons for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.cm,right=1.cm,top=1.25cm,bottom=1.25cm,columnsep=0.25cm,footskip=1.5\baselineskip}

\usepackage{lastpage}
\usepackage{fancyhdr}
\fancyhf{}
\renewcommand{\headrule}{}
\fancyfoot[R]{\footnotesize \thepage /\pageref{LastPage}}
\AtBeginDocument{\pagestyle{fancy}}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

%\usepackage[hyphens]{url}
%\usepackage{hyperref}


% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
% WHEN COMPILING WITH XELATEX PLEASE USE
% xelatex -shell-escape -output-driver="xdvipdfmx -z 0" sample.tex
\iftutex 
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{000000}%{2E2E2E}
\definecolor{LightGrey}{HTML}{000000}%{666666}
\definecolor{DarkPastelRed}{HTML}{000000}%{450808}
\definecolor{PastelRed}{HTML}{458EF7}%{8F0D0D}
\definecolor{GoldenEarth}{HTML}{000000}%{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}
% ...and the markers for the date/location for \cvevent
% \renewcommand{\cvDateMarker}{\faCalendar*[regular]}
% \renewcommand{\cvLocationMarker}{\faMapMarker*}


% If your CV/résumé is in a language other than English,
% then you probably want to change these so that when you
% copy-paste from the PDF or run pdftotext, the location
% and date marker icons for \cvevent will paste as correct
% translations. For example Spanish:
% \renewcommand{\locationname}{Ubicación}
% \renewcommand{\datename}{Fecha}


%% Use (and optionally edit if necessary) this .tex if you
%% want to use an author-year reference style like APA(6)
%% for your publication list
% When using APA6 if you need more author names to be listed
% because you're e.g. the 12th author, add apamaxprtauth=12
% \usepackage[backend=biber,style=apa6,sorting=ydnt]{biblatex}
% \defbibheading{pubtype}{\cvsubsection{#1}}
% \renewcommand{\bibsetup}{\vspace*{-\baselineskip}}
% \AtEveryBibitem{%
%   \makebox[\bibhang][l]{\itemmarker}%
%   \iffieldundef{doi}{}{\clearfield{url}}%
% }
% \setlength{\bibitemsep}{0.25\baselineskip}
% \setlength{\bibhang}{1.25em}

%% Use (and optionally edit if necessary) this .tex if you
%% want an originally numerical reference style like IEEE
%% for your publication list
\usepackage[backend=biber,style=ieee,sorting=ydnt,defernumbers=true]{biblatex}
%% For removing numbering entirely when using a numeric style
\setlength{\bibhang}{1.25em}
\DeclareFieldFormat{labelnumberwidth}{\makebox[\bibhang][l]{\itemmarker}}
\setlength{\biblabelsep}{0pt}
\defbibheading{pubtype}{\cvsubsection{#1}}
\renewcommand{\bibsetup}{\vspace*{-\baselineskip}}
\AtEveryBibitem{%
  \iffieldundef{doi}{}{\clearfield{url}}%
}

%% sample.bib contains your publications
\addbibresource{LaurentNtibarikureResume.bib}
% \usepackage{academicons}\let\faOrcid\aiOrcid
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\name{Laurent Ntibarikure}
\tagline{Engineering Systems | Physical Modeling | Customer Focus}
%% You can add multiple photos on the left or right
% \photoR{2.8cm}{LaurentNtibarikure.jpg}
% \photoL{2.5cm}{LaurentNtibarikure.jpg}

\personalinfo{%
  % Not all of these are required!
  % \email{user@email.com}
  % \phone{+31-123-456-789}
  % \mailaddress{}
  \homepage{ntilau.github.io}
  % \twitter{@twitterhandle}
  % \xtwitter{@ntilau}
  \linkedin{ntilau}
  \github{ntilau}
  % \orcid{0009-0006-4601-3618}
  \location{Eindhoven, Netherlands}
  %% You can add your own arbitrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}[https://example.com/]

  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
  %%
  %% For services and platforms like Mastodon where there isn't a
  %% straightforward relation between the user ID/nickname and the hyperlink,
  %% you can use \printinfo directly e.g.
  % \printinfo{\faMastodon}{@username@instace}[https://instance.url/@username]
  %% But if you absolutely want to create new dedicated info fields for
  %% such platforms, then use \NewInfoField* with a star:
  % \NewInfoField*{mastodon}{\faMastodon}
  %% then you can use \mastodon, with TWO arguments where the 2nd argument is
  %% the full hyperlink.
  % \mastodon{@username@instance}{https://instance.url/@username}
}

\makecvheader
%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.65}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}
\cvsection{Summary}
My experiences, with a focus on numerical methods, encompass electronic and
mechatronic system development and technical sales \& support across several
industries (Energy \& Aerospace, Electronic Design Automation, and Semiconductors).

\medskip

Leveraging such a background, I am currently helping designers to develop more
effectively towards system-level compliance.

\cvsection{Experience}

\cvevent{Sr Engineer -- Design Enablement}{NXP Semiconductors}{03/2022 -- Present}{Eindhoven, Netherlands}
\begin{itemize}
\item Implemented electromagnetic simulation flows for SoCs development and electromagnetic interference
predictions.
\item Enhanced vendor solutions to meet the design and integration requirements of the cloud platform.
\item Developed problem-resolution automation scripts and applied AI/ML algorithms for
electromagnetic surrogate models.
\end{itemize}
\divider

\cvevent{Technical Account Manager}{Ansys}{03/2020 -- 03/2022}{Utrecht, Netherlands}
\begin{itemize}
\item Drove customer satisfaction by providing multi-disciplinary technical support and
managing global presales activities for the Ansys portfolio.
\item Led teams to architect flows across disciplines, focusing on requirements and
critical success factors.
\item Advised global sales and account engineers on addressable initiatives and pipelines
with preliminary requirements and solutions visions.
\end{itemize}
\divider

\cvevent{Sr. Applications Engineer}{Ansys}{01/2019 -- 03/2020}{Utrecht, Netherlands}
\begin{itemize}
\item Executed presales activities for electronic systems across industries, supporting
high frequency solutions and EMC flows across EMEA.
\item Led technical alignment with customers on automotive electrification and
connectivity projects, successfully delivering consulting services and trainings.
\end{itemize}
\divider

\cvevent{Lead Engineer -- Testing}{Baker Hughes}{06/2013 -- 12/2018}{Florence, Italy}
\begin{itemize}
\item Led the development of industrial, ATEX compliant, distributed data acquisition
systems to streamline tests execution timelines from months to weeks.
\item Resolved 5+ electromagnetic interference issues in NPI validations and factory
acceptance tests, contributing to best practices.
\item Received an innovation award for patent disclosure of the Structural Vibration
Monitoring System and multiple rewards for innovative solutions and customer impact.
\end{itemize}
\divider

\cvevent{Startup Co-founder}{Universit\`a degli Studi di Firenze}{06/2012 -- 06/2013}{Florence, Italy}
\begin{itemize}
\item Initiated a spin-off, ElectroSoft, to provide efficient numerical codes for design problems.
\item Led team promotion and value proposition pitches to business angels.
\item Developed first opportunities in the defense industry.
\end{itemize}
\divider

\cvevent{Doctoral Researcher}{Universit\`a degli Studi di Firenze}{01/2011 -- 06/2013}{Florence, Italy}
\begin{itemize}
\item Researched applied \& computational electromagnetics, presenting 10+ papers, advising student theses, and supporting examinations.
\item Developed high-frequency electromagnetics 3D finite element C++ code for domain decomposition and nonlinear formulations.
\item Architected a methodology using MathWorks Simulink and Ansys HFSS for electromagnetic compatibility in variable speed drive systems.
\end{itemize}
\divider

\cvevent{Visiting Researcher}{Universit\"at des Saarlandes}{10/2009 -- 02/2010}{Saarbr\"ucken, Germany}
\begin{itemize}
\item Developed model order reduction in finite element analysis of antenna arrays for fast and accurate beamforming.
\item Implemented Matlab code for a 3000x matrix reduction and 300x speedup in antenna pattern computation
\end{itemize}
\divider

\cvevent{R\&D Engineer}{Universit\`a degli Studi di Firenze}{12/2007 -- 03/2008}{Florence, Italy}
\begin{itemize}
\item Developed wireless connectivity for a battery-powered avalanche rescue ground penetrating radar, optimizing firmware for fast full-duplex/half-duplex conversion timing.
\item Executed the design and assembly of an ISM 868 MHz serial modem PCB prototype with off-the-shelf MCU and Radio (sub-GHz RFFE).
\item Achieved successful wireless system resulting in improved signal detection accuracy.
\end{itemize}

\cvsection{Projects}

\cvevent{Bearings loading test rig}{Baker Hughes, a GE Company}{05/2018 - 12/2018}{Florence, Italy}
\begin{itemize}
  \item Conceptual design of a novel bearings loading test rig aimed at validating bearings NTIs. 
  \item Investigated on modeling methods of EM coupling between power (variable speed drive system) 
  and signals cabling systems to predict potential interference issues.
\end{itemize}
\divider

\cvevent{GE Aviation’s Catalyst}{Baker Hughes, a GE Company}{06/2017 - 12/2018}{Prague, Czech Republic}
\begin{itemize}
  \item Led special instrumentation design and global technical reviews of FETT with design
and testing teams (Czech Rep., Poland, USA, Canada).
  \item Contributed to >4 M\$ cross-P\&L project and customer satisfaction.
\end{itemize}
\divider

\cvevent{Gas Turbine embedded SAW sensors}{Baker Hughes, a GE Company}{02/2018 - 12/2018}{Florence, Italy}
\begin{itemize}
\item Collaborated with University of Florence to investigate the high-frequency numerical modeling of SAW sensors for the accuracy control of temperature measurements.
\end{itemize}
\divider

\cvevent{LM9000: 65 MW aeroderivative gas turbine}{Baker Hughes, a GE Company}{06/2018 - 12/2018}{Florence, Italy}
\begin{itemize}
\item Contributed to conceptual instrumentation design and test rigs erection, data
acquisition architecture and control system design by technical and HAZOP reviews.
\end{itemize}
\divider

\cvevent{Cross'd}{}{01/2018 - 11/2018}{Florence, Italy}
\begin{itemize}
\item Social networking app PoC based on Bluetooth Low Energy ranging. PoC with Apache
Cordova and an AWS EC2 instance
\end{itemize}
\divider

\cvevent{BLE Asset Tracking}{}{07/2017 - 09/2017}{Florence, Italy}
\begin{itemize}
\item Sub 5\$/Unit PoC of BLE tags (TI's CC2640) with firmware optimized for long-battery
life, aimed at asset tracking and inventory management
\end{itemize}
\divider

\cvevent{GE Power slip-ring digital telemetry}{Universit\"at des Saarlandes}{04/2017 - 05/2017}{Saarbr\"ucken, Germany}
\begin{itemize}
\item Ran Ansys HFSS simulations to optimize signal integrity over slip-ring connections
(power supply and ethernet transmission lines) 
\item Achieved shrinking of the rings spacing leading to manufacturing costs reduction
\item 4 weeks-FTE cross-P\&L billing and customer satisfaction
\end{itemize}
\divider

\cvevent{Wet gas compressors at KLAB}{GE Oil \& Gas}{02/2016 - 06/2016}{Haugesund, Norway}
\begin{itemize}
\item Designed and procured validation equipment for ATEX zone 1 test bench. 
\item Developed Ex-d antenna and low noise amplifier system for GPS synchronization on NI's PXI systems. 
\item Managed IEC 60079-11 simple apparatus compliance on load cells upon using
extremely low voltage (1.5 V) Ex-ia Wheatstone bridge conditioners.
\end{itemize}
\divider

\cvevent{Power density compressor}{GE Oil \& Gas}{03/2014 - 05/2016}{Florence, Italy}
\begin{itemize}
\item Led the commissioning Fieldbus Foundation use in testing lab for more than 240 pressure transducers (0.1\% uncertainty) 
upon identifing the proper Firmware configuration which enabled for massive and accurate pressure measurements.
\item Managed capacitive vibration probes ATEX-compliance. 
\item Developed electrostatic numerical model to predict capacitance variation in various surroundings and target shape conditions. 
\item Contributed to DM37/08 compliance of the test rig contract specification, including power and signaling cabling selection and proper installation.
\end{itemize}
\divider

\cvevent{SNC1-2 steam turbine performance evaluation in 6.2 MW cogeneration plant}{GE Oil \& Gas}{09/2015 - 04/2016}{Florence, Italy}
\begin{itemize}
\item Defined novel pressure hookups method at lower cost and better performance to achieve accuracy controlled inter-stage enthalpy measurements 
according to ASME PTC 19.11. 
\item Programmed a CAN to Modbus TCP embedded module to enable static torque measurements on a MagCanica telemetry.
\end{itemize}
\divider

\cvevent{GE-6G PowerGen Module Structural Vibrations Monitoring System}{GE Oil \& Gas}{11/2015 - 03/2016}{Saarbr\"ucken, Germany}
\begin{itemize}
\item Project involving ATEX-compliant distributed acquisition system for more than 150 vibration measurement points, 
with 40 kHz analog bandwidth, WiFi5 backhaul to storage and real-time monitoring, 
GPS or daisy-chain clock distribution synchronization \& TSN investigation, 
characterized of 3D models \& BOM detailed design re-insourcing for timely delivery and cost optimization of 
certified equipment in less than 4 months (vs typ. 8 months). 
This also led to the introduction and consolidation of a software based velocity and displacement 
real-time computation from accelerometers, achieving direct \$150k savings, and subsequent lab processes OPEX improvements. 
Customer value delivered as onsite Turbomachinery Modules structural commissioning.
\end{itemize}
\divider

\cvevent{NovaLT16 gas turbine, bearings and cooling component tests}{GE Oil \& Gas}{04/2014 - 10/2015}{Saarbr\"ucken, Germany}
\begin{itemize}
\item Design and validation of smartbox (field datalogger) for analog signals. 
\item Defined EMC-aware measurement loops design to achieve noise immunity and enhanced measurement accuracies, 
rigorously applying EN 61000 guidelines (CENELEC 25).
\end{itemize}
\divider

\cvevent{GE Aviation’s GE9X High Pressure Compressor}{GE Oil \& Gas}{01/2014 - 04/2014}{Massa, Italy}
\begin{itemize}
\item High density data acquisition system design for GE Aviation’s compressor test in Massa. 
\item Performed mitigation on EMC noise due to 130 kW variable speed ventilation system
\end{itemize}
\divider

\cvevent{BCL306 and BCL317 centrifugal compressors rotordynamics}{GE Oil \& Gas}{06/2013 - 03/2014}{Florence, Italy}
\begin{itemize}
\item Performed an Ex-p execution of stability’s magnetic exciter, contributed to the
resolution of customer’s opened nonconformity on rotordynamic vibrations upon
conducting an electromagnetic interference on Bently Nevada's 3500 RCA.
\end{itemize}
\divider

\cvevent{\href{https://github.com/ntilau/FES}{Finite Elements Software (FES)}}{Universit\`a degli Studi di Firenze}{06/2011 - 02/2014}{Florence, Italy}
\begin{itemize}
\item FES is an open source C++ framework for the development of "ad-hoc" simulation
software aimed at a rapid implementation of novel numerical methods based on the
Galerkin method. Core formulations validated reusing meshes from commercial
packages (Comsol, HFSS)
\end{itemize}
\divider

\cvevent{Spectral domain FEM model order reduction}{Universit\"at des Saarlandes}{10/2009 - 02/2010}{Saarbr\"ucken, Germany}
\begin{itemize}
\item Developed in Matlab efficient near-to-far-fields formulations for fast electromagnetic radiation computation in large finite elements problems exploiting model order
reduction with spectral interpolation for beam steering and pattern angles
\item Modeled a large patch antenna array, assessing accuracy and performances through mesh/model export from Ansoft HFSS v11
\end{itemize}
\divider

\cvevent{RS-232 modem in ISM 868 MHz band}{University of Florence}{01/2007 - 04/2007}{Florence, Italy}

\begin{itemize}
    \item Designed and prototyped an 868 MHz wireless link for a ground penetration radar
remote control over RS-232 protocol
\item C-coded the PIC microcontroller FW and
optimized in Assembly to garantee the full-duplex operation over half-duplex TI’s
CC1100 radio. 
\item Evaluated the performance of the wireless link in open field
\end{itemize}


%\cvsection{A Day of My Life}

% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
%\wheelchart{1.5cm}{0.5cm}{%
%  6/8em/accent!30/{Sleep,\\beautiful sleep},
%  3/8em/accent!40/Hopeful novelist by night,
%  8/8em/accent!60/Daytime job,
%  2/10em/accent/Sports and relaxation,
%  5/6em/accent!20/Spending time with family
%}

% use ONLY \newpage if you want to force a page break for
% ONLY the current column
%\newpage

%%%%%%%%%%%%%%%%%%%%%%
%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

%%% 
\cvsection{Education}
\cvevent{Doctor of Philosophy - PhD, Electronics Engineering}{Universit\`a degli Studi di Firenze}{01/2011 -- 02/2014}{Florence, Italy}
School of "RF, Microwaves and Electromagnetics". Computational Methods focus. With grant (Jan 2011 - Jun 2013).

\divider

\cvevent{Master's Degree, Electronics Engineering}{Universit\`a degli Studi di Firenze}{10/2007 -- 04/2010}{Florence, Italy}
Erasmus Placement/LLP framework thesis semester at Universit\"at des Saarlandes.
With grant (Sep 2009 - Mar 2010).

\divider

\cvevent{Bachelor's degree, Electrical and Electronics Engineering}{Universit\`a degli Studi di Firenze}{01/2003 - 04/2008}{Florence, Italy}

%%%
\cvsection{Awards}

\cvachievement{\faTrophy}{EMEA TAM of the Year | Ansys (01/2021)}{Award for customer and industry focus}
\divider

\cvachievement{\faHeartbeat}{Learn and adapt to win | BHGE (07/2018)}
{Patent impact award for the disclosure of "Module with sensors arrangement"}
\divider

\cvachievement{\faHeartbeat}{Customers determine our success | BHGE (03/2017)}
{Bronze award for the GE Aviation's Catalyst FETT advanced test instrumentation consulting}
\divider

\cvachievement{\faHeartbeat}{Customers determine our success | GE (10/2016)}
{Bronze award for the successful execution of the vibration monitoring system ZADCO customer structural vibrations acceptance tests}
\divider

\cvachievement{\faHeartbeat}{Learn and adapt to win | GE (03/2016)}
{Bronze award for the co-generation plant cost savings on the SNC1-2 steam turbine performance validation}
\divider

\cvachievement{\faHeartbeat}{Learn and adapt to win | GE (10/2015)}
{Bronze award for the introduction and validation of an effective, cost-saving, structural vibrations digital integration algorithm aimed at accurately deriving speed \& displacements measurements from ATEX-compliant accelerometers}
\divider

\cvachievement{\faHeartbeat}{External focus | GE (06/2014)}
{Bronze award for the RCA activities on Cessao Onerosa, ADRE monitoring system EMI noise mitigation and customer assurance}
\divider

\cvachievement{\faTrophy}{Giorgio Barzilai Prize | SIEm (09/2012)}
{Best paper award for young researchers, for the work "Model order reduction in Finite Element analysis of phased array antennas" presented at the XIX RiNEm}
\divider

\cvachievement{\faHeartbeat}{Ph.D. studies grant | UniFi (12/2010)}
{Full tuition fees and allowance for research on Electromagnetic Compatibility modeling techniques in variable speed drive systems - with GE/Nuovo Pignone}
\divider

\cvachievement{\faHeartbeat}{Dean's listing | UniFi (04/2010)}
{Commissione di Laurea Specialistica in Ingegneria Elettronica presieduta dal Prof. Piero Tortoli (Prot. 1051 n. class. III/9.1.2 del 24 Maggio 2010)}
\divider

\cvachievement{\faHeartbeat}{LLP/Erasmus Placement grant | UniFI (10/2009)}
{Thesis work semester relocation support at Universit\"at des Saarlandes}

%%%
\cvsection{Certification}
\cvachievement{\faFile}{Professional Engineer, ID:ES2010277049000038}{Universit\`a degli Studi di Firenze}

%%%
\cvsection{Courses}
\cvevent{Command of the Message}{Ansys}{06/2020}{Remote}
\medskip
\cvevent{JAWS: Just Another Way of Selling}{Ansys}{02/2020}{Paris, France}
\medskip
\cvevent{GE Crotonville: Delivering Customer Impact}{GE Oil \& Gas}{03/2016}{Munich, Germany}
\medskip
\cvevent{Total Quality Lean Six Sigma Green Belt}{GE Oil \& Gas}{06/2014}{Florence, Italy}

%%%
\cvsection{Skills}

% Don't overuse these \cvtag boxes — they're just eye-candies and not essential. If something doesn't fit on a single line, it probably works better as part of an itemized list (probably inlined itemized list), or just as a comma-separated list of strengths.

% The `ragged2e` document class option might cause automatic linebreaks between \cvtag to fail.
% Either remove the ragged2e option; or 
% add \LaTeXraggedright in the paragraph for these \cvtag
{\LaTeXraggedright
%\cvtag{Hard-working}
%\cvtag{Eye for detail}
%\cvtag{Motivator \& Leader}
\cvtag{Engineering}
\cvtag{Simulations}
\cvtag{Management}
\cvtag{Testing}
\cvtag{Sales}
\cvtag{Strategy}
\cvtag{Leadership}
\cvtag{Customer Satisfaction}
\cvtag{Finite Element Analysis}
\cvtag{RF}
\cvtag{Electronics}
\cvtag{Semiconductors}
\cvtag{Scripting}
\cvtag{Matlab}
\cvtag{C++}
\cvtag{C}
\cvtag{Python}
\par}

%\divider\smallskip

%% ...Or manually add linebreaks yourself
%\cvtag{C++}
%\cvtag{Embedded Systems}\\
%\cvtag{Statistical Analysis}

\cvsection{Languages}
\cvskill{Dutch}{1}
\divider
\cvskill{English}{4}
\divider
\cvskill{French}{5} %% Supports X.5 values.
\divider
\cvskill{German}{1}
\divider
\cvskill{Italian}{5}
\divider
\cvskill{Kirundi}{5}
\divider
\cvskill{Spanish}{3} %% Supports X.5 values.

%% Yeah I didn't spend too much time making all the
%% spacing consistent... sorry. Use \smallskip, \medskip,
%% \bigskip, \vspace etc to make adjustments.
%\medskip

%\cvsection{My Life Philosophy}

%\begin{quote}
%``Something smart or heartfelt, preferably in one sentence.''
%\end{quote}

%%%
%\cvsection{References}

% \cvref{name}{email}{mailing address}
%\cvref{Prof.\ Alpha Beta}{Institute}{a.beta@university.edu}{Address Line 1\\Address line 2}

%\divider

%\cvref{Prof.\ Gamma Delta}{Institute}{g.delta@university.edu}{Address Line 1\\Address line 2}

\cvsection{Publications}

%% Specify your last name(s) and first name(s) as given in the .bib to automatically bold your own name in the publications list.
%% One caveat: You need to write \bibnamedelima where there's a space in your name for this to work properly; or write \bibnamedelimi if you use initials in the .bib
%% You can specify multiple names, especially if you have changed your name or if you need to highlight multiple authors.
\mynames{Lim/Lian\bibnamedelima Tze,
  Wong/Lian\bibnamedelima Tze,
  Lim/Tracy,
  Lim/L.\bibnamedelimi T.}
%% MAKE SURE THERE IS NO SPACE AFTER THE FINAL NAME IN YOUR \mynames LIST

\nocite{*}

\printbibliography[heading=pubtype,title={\printinfo{\faFile*[regular]}{Patents}},type=patent]

\divider

\printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

\divider

\printbibliography[heading=pubtype,title={\printinfo{\faFile*[regular]}{Journal Articles}},type=article]

\divider

\printbibliography[heading=pubtype,title={\printinfo{\faUsers}{Conference Proceedings}},type=inproceedings]



\end{paracol}


\end{document}
